### 2013-09-28 doc/chapters/usage.tex
briefly explain the ./createmodel script

@@

Explain how to write a FlexibleSUSY model file (starting from a SARAH
model file).

A FlexibleSUSY model file is a Mathematica file, where the following
pieces are defined:

@@

\subparagraph{FSModelName}
Name of the FlexibleSUSY model.
Example (MSSM):
\begin{lstlisting}[language=Mathematica]
FSModelName = "MSSM";
\end{lstlisting}

@@

\paragraph{Constraints}
Currently three constraints are supported: low-scale, susy-scale and
high-scale constraints.  In FlexibleSUSY they are named as
\code{LowScale}, \code{SUSYScale} and \code{HighScale}.  For
each constraint there is a scale definition (named after the
constraint), an initial guess for the scale (concatenation of the
constraint name and \code{FirstGuess}) and a list settings to be
applied at the constraint (concatenation of the constraint name and
\code{Input}).
\\
Example (MSSM):
\begin{lstlisting}[language=Mathematica]
(* susy-scale constraint *)
SUSYScale = Sqrt[M[Su[1]]*M[Su[6]]];        (* scale definition *)
SUSYScaleFirstGuess = Sqrt[m0^2 + 4 m12^2]; (* first scale guess *)
SUSYScaleInput = {};                        (* nothing is set here *)

@@

\begin{sidewaystable}[tb]
  \centering
  \begin{tabularx}{\textwidth}{>{\ttfamily}l>{\ttfamily}lX}
    \toprule
    variable    & default value & description \\
    \midrule
    FSModelName & Model`Name & Name of the FlexibleSUSY model \\
    OnlyLowEnergyFlexibleSUSY & False & low-energy model \\
    MINPAR & \{\} & list of input parameters in SLHA MINPAR block \\
    EXTPAR & \{\} & list of input parameters in SLHA EXTPAR block \\
    DefaultParameterPoint & \{\} & list of default values for the input parameters \\
    LowScale & SM[MZ] & Standard Model matching scale (in GeV) \\
    LowScaleFirstGuess & SM[MZ] & first guess for the Standard Model matching scale (in GeV) \\
    LowScaleInput & \{\} & settings applied at the low scale \\
    SUSYScale & 1000 & scale of supersymmetric particle masses (in GeV) \\
    SUSYScaleFirstGuess & 1000 & first guess for the susy scale (in GeV) \\
    SUSYScaleInput & \{\} & settings applied at the susy scale \\
    HighScale & SARAH`hyperchargeCoupling == SARAH`leftCoupling
      & unification scale (in GeV) \\
    HighScaleFirstGuess & $10^{14}$ & first guess for the unification scale (in GeV) \\
    HighScaleInput & \{\} & settings applied at the unification scale \\
    \bottomrule
  \end{tabularx}
  \caption{FlexibleSUSY model file variables}
  \label{tab:model-file-variables}
\end{sidewaystable}

@@

Explain how to write a custom makefile module (module.mk) for a
FlexibleSUSY model.

>>>>

\subsubsection{\code{createmodel}}

The \code{createmodel} script sets up a \flexisusy\ model.  This involves
%
\begin{itemize}
\item a model directory \code{models/<flexiblesusy-model>/}
\item a makefile module \code{models/<flexiblesusy-model>/module.mk}
\item a \flexisusy\ model file \code{models/<flexiblesusy-model>/FlexibleSUSY.m}
\item a Mathematica start script \code{models/<flexiblesusy-model>/start.m}
\end{itemize}
%
Usage:
\begin{lstlisting}[language=bash]
./createmodel --models=<flexiblesusy-model>:<sarah-model>
\end{lstlisting}
Here \code{<flexiblesusy-model>} is the name of \flexisusy\ model
to be created and \code{<sarah-model>} is the name of the \sarah\
model file which defines the Lagrangian and the particles.\\
Example:
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM
\end{lstlisting}
%
Multiple models can be created at once by separating the models by a
comma.\\
Example:
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM,MyCNMSSM:NMSSM
\end{lstlisting}
%
If a certain \sarah\ sub-model should be used, the name of the sub-model
has to be appended with at preceeding slash.\\
Example: use the \code{CKM} sub-model of the \code{MSSM}
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM/CKM
\end{lstlisting}
%
For further information and options see
\begin{lstlisting}[language=bash]
./createmodel --help
\end{lstlisting}

@@

Explain how to write a \flexisusy\ model file (starting from a \sarah\
model file).

A \flexisusy\ model file is a Mathematica file, where the following
pieces are defined:

@@

\subparagraph{FSModelName}
Name of the \flexisusy\ model.
Example (MSSM):
\begin{lstlisting}[language=Mathematica]
FSModelName = "MSSM";
\end{lstlisting}

@@

\paragraph{Constraints}
Currently three constraints are supported: low-scale, susy-scale and
high-scale constraints.  In \flexisusy\ they are named as
\code{LowScale}, \code{SUSYScale} and \code{HighScale}.  For
each constraint there is a scale definition (named after the
constraint), an initial guess for the scale (concatenation of the
constraint name and \code{FirstGuess}) and a list settings to be
applied at the constraint (concatenation of the constraint name and
\code{Input}).
\\
Example (MSSM):
\begin{lstlisting}[language=Mathematica]
(* susy-scale constraint *)
SUSYScale = Sqrt[M[Su[1]]*M[Su[6]]];        (* scale definition *)
SUSYScaleFirstGuess = Sqrt[m0^2 + 4 m12^2]; (* first scale guess *)
SUSYScaleInput = {};                        (* nothing is set here *)

@@

\begin{sidewaystable}[tb]
  \centering
  \begin{tabularx}{\textwidth}{>{\ttfamily}l>{\ttfamily}lX}
    \toprule
    variable    & default value & description \\
    \midrule
    FSModelName & Model`Name & Name of the \flexisusy\ model \\
    OnlyLowEnergyFlexibleSUSY & False & low-energy model \\
    MINPAR & \{\} & list of input parameters in SLHA MINPAR block \\
    EXTPAR & \{\} & list of input parameters in SLHA EXTPAR block \\
    DefaultParameterPoint & \{\} & list of default values for the input parameters \\
    LowScale & SM[MZ] & Standard Model matching scale (in GeV) \\
    LowScaleFirstGuess & SM[MZ] & first guess for the Standard Model matching scale (in GeV) \\
    LowScaleInput & \{\} & settings applied at the low scale \\
    SUSYScale & 1000 & scale of supersymmetric particle masses (in GeV) \\
    SUSYScaleFirstGuess & 1000 & first guess for the susy scale (in GeV) \\
    SUSYScaleInput & \{\} & settings applied at the susy scale \\
    HighScale & SARAH`hyperchargeCoupling == SARAH`leftCoupling
      & unification scale (in GeV) \\
    HighScaleFirstGuess & $10^{14}$ & first guess for the unification scale (in GeV) \\
    HighScaleInput & \{\} & settings applied at the unification scale \\
    \bottomrule
  \end{tabularx}
  \caption{\flexisusy\ model file variables}
  \label{tab:model-file-variables}
\end{sidewaystable}

@@

Explain how to write a custom makefile module (module.mk) for a
\flexisusy\ model.
